\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-24 paper.tex
Modify trading model and remove figures

One can create multiple channels, however, the size of a channel is fixed which is decided before creation. Thus data providers need to firstly decide how to distribute data product into MAM channels. While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system. See Figure \ref{fig:launching_product}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}

@@

\subsection{Launching and Searching Products}
To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and product contract. Each product has a product contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{key_certification}
    \caption{Session key certification process with blind signature.}
    \label{fig:key_certification}
\end{figure}

@@

\subsection{Trading}
The entire trading process is as shown in Figure \ref{fig:trading_product}. Once a consumer who wants to subscribe certain streaming data that is generated  pays a subscription fee to the product contract, he/she is added to the consumers list automatically by the smart contract.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{trading_product}
    \caption{The process for the product trading.}
    \label{fig:trading_product}
\end{figure}

Next, session key $k$ should be exchanged between the data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider can obtain public keys of each consumer from the registration contract. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{key_exchange}
    \caption{Session key exchange process between the data provider and consumer.}
    \label{fig:key_exchange}
\end{figure}

>>>>

One can create multiple channels, however, the size of a channel is fixed which is decided before creation. Thus data providers need to firstly decide how to distribute data product into MAM channels. While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system.

@@

\subsection{Launching and Searching Products}
To sell streaming data, a data provider needs to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and product contract. Each product has a product contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers. When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{key_certification_exchange}
    \caption{Session key certification with blind signature and session key exchange.}
    \label{fig:key_certification_exchange}
\end{figure}

@@

\subsection{Trading}
Once a consumer who wants to subscribe certain streaming data that is generated  pays a subscription fee to the product contract, he/she is added to the consumers list automatically by the smart contract.

Next, session key $k$ should be exchanged between the data provider and consumers. The data provider can obtain public keys of each consumer from the registration contract. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to obtain the session key $k$ and signature $Sign(k)$.
